\documentclass{article}

\usepackage{times}
\usepackage{fullpage}
\usepackage{eprint}
\usepackage{rotating}
\usepackage{eepic}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{amsthm}

%\tocdetails{%
%   volume=0, number=5, year=2005, firstpage=78,
%   received={October 15, 2004}, 
%   published={December 31, 2004}
%}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
%\newtheorem{idea}{Idea}[section]

%\theoremstyle{definition}
%\newtheorem{thought}[theorem]{Thought}
%\newtheorem{thought}{Thought}[section]

\title{Quantum Compiling with the Super-Kitaev Algorithm}
\date{November 2nd, 2010}
\author{Paul Pham}

\input{Qcircuit}

\begin{document}

%\newcommand{\ket}[1]{|#1 \rangle}
%\newcommand{\bra}[1]{\langle #1 |}
\newcommand{\braket}[2]{\langle #1|#2 \rangle}
\newcommand{\normtwo}{\frac{1}{\sqrt{2}}}
\newcommand{\norm}[1]{\parallel #1 \parallel}

\maketitle

\section{Introduction}

When describing a quantum algorithm, we use a high-level formalism of
gates operating on qubits in the quantum circuit model.
We can treat gates operating on an $n$-qubit quantum computer as unitary
matrices of dimension $2^n \times 2^n$ with unit determinant.
However, in experimental settings,
we can only perform some gates efficiently, and these are usually local,
2-qubit operations. Moreover, most of our results for fault-tolerant
quantum computing in the presence of noise stipulates that we have a finite
number of universal gates we can perform with some limited precision.

How then, do we translate our quantum algorithms into something that can run
on hardware? In analogy to classical computers, we describe this translation
as {\em quantum compiling}. One of the central results of quantum computing,
and the reason why it is interesting, is that we can actually perform this
quantum compiling efficiently. This first result is called the
Solovay-Kitaev theorem \cite{Dawson2005}, which provides an efficient way to
approximate any quantum gate. I presented this algorithm in an earlier talk, but
I'll briefly review the results here. However, the constants for this method
scale exponentially with the number of qubits and involve an intractably
large preprocessing step.

The second result is more recent but much less well-known, and is called
the Super-Kitaev algorithm (named by Aram Harrow). This new method improves upon
the bounds for compiled circuit size over the normal Solovay-Kitaev algorithm,
but comparison is more complicated. Super-Kitaev introduces some new tradeoffs to the
comparison, such as ancillary qubits and classical postprocessing. In doing so,
Kitaev also gives us some interesting modules which are worth studying for
their own sake. In these notes, we will outline the Super-Kitaev algorithm at
a high-level to develop some intuition about why it works, describe how we 
might implement it in practice.

\section{Definitions}

\subsection{Approximation vs. Simulation}

I'll use the terms "approximation" and "simulation" interchangeably, as in
a quantum compiler will take an input circuit and produce as output a new
circuit which approximates or simulates the original circuit to some degree
of precision.

\subsection{Standard Set}

We use the following standard set $\mathcal{Q}$ from \cite{ksv02}

\begin{equation}
\mathcal{Q} = \{ H, K, K^{-1}, \Lambda(\sigma^x), \Lambda^2(\sigma^x) \}
\end{equation}

where these gates are defined as follows:

\begin{equation*}
H = \normtwo \left(
  \begin{array}{cc}
    1 & 1 \\
    1 & -1 \\
  \end{array} \right)
\end{equation*}

\begin{equation*}
K = \left(
  \begin{array}{cc}
    1 & 0 \\
    0 & i \\
  \end{array} \right)
\end{equation*}

Even though realistic implementations of a quantum computer may have a different
set of hardware instructions, Kitaev's analysis assumes that the standard set
can always be efficiently compiled down further into this hardware set.

Note that this may not be valid. For example, in order for ion traps to perform
even a Hadamard gate to any precision requires a combination of $\sigma^x$ and
$\sigma^z$ gates. However, we won't let this bother us for now.

\subsection{Parameters}

For these notes, we restrict ourselves to $d=2^n$ for an $n$-qubit system (qudits)
and consider the problem of compiling an entire circuit $C$ of $L$ gates with depth
$d$ to a new, compiled circuit $C'$ of size $L'$ and depth $d'$ which approximates
$C$ within some error. There is some overhead in the compiled circuit, so in
general $C'$ is larger (that is, $L' > L$ and $d' > d$). It's also known that
in order to approximate a circuit with $L$ gates to a total precision of $\epsilon$
requires each gate to be approximated to a precision of $L/\epsilon$, which requires
the following number of gates. We'll find this $l$ parameter useful in describing the compiler overheads of
both the Solovay-Kitaev and Super-Kitaev methods.

Why do we care about depth? This gives us a heuristic for how ``parallelized'' our
circuit is. If we flatten our circuit into layers $\{l_i\}$, where each layer $l_i$
is dependent only on inputs from the previous layer $l_{i-1}$ and produces
only outputs to the next layer $l_{i+1}$, then all the gates within the layer
$l_i$ can be performed in parallel. All other things being equal, a circuit with low depth will complete
faster than one with high depth, although in practice we can only execute
fixed-width circuits.

Also, when running the compiler, there are several time resources to consider.
The first is classical preprocessing time, denoted $T_{pre}$, which is a way of optimizing
the generated quantum circuit by spending more classical resources upfront.
The second is classical postprocessing time, denoted $T_{post}$, which likewise
is meant to reduce the size of the quantum circuit but depends on quantum
measurements and may be fed back into future quantum operations later.

A summary of these parameters are provided below:

\begin{tabular}{|c|c|}
\hline
$d$ & dimension of quantum gates (matrix representation)\\
$\epsilon$ & the desired accuracy of the compiled circuit\\
$L$ & size of input circuit to be compiled, in gates from $\mathcal{Q}$\\
$d$ & depth of input circuit to be compiled\\
$L'$ & size of compiled output circuit, in gates from $\mathcal{Q}$\\
$d'$ & depth of compiled circuit to be compiled\\
$n$ & $=O(\log{L/\epsilon})$, shorthand parameter for asymptotic analysis\\
$T$ & classical running time of the compiling algorithm\\
$T_{pre}$ & classical preprocessing time, before the compiler is run\\
$T_{post}$ & classical postprocessing time, after the compiler is run or during\\
\hline
\end{tabular}

\subsection{Universal Instruction Sets and Compiled Sequences}
More formally, suppose we have a universal instruction set $\mathcal{G}$ which
contains some finite number of gates $g \in SU(d)$ and also their inverses $g^\dagger$.
$\mathcal{G}$ is universal for $SU(d)$ in that it generates a dense subgroup.
In other words, given an arbitrary quantum gate $U \in SU(d)$ and a desired
accuracy $\epsilon$ we can find a product $S=g_1 \cdots g_m$ from $\mathcal{G}$
which approximates $U$ to within $\epsilon$ using some distance function.

We can either use the matrix operator norm to define the distance function
such as:

\begin{equation}
d(U,S) \equiv \norm{U - S} \equiv \sup_{\norm{\ket{\psi}}=1} \norm{(U-S)\ket{\psi}} < \epsilon
\end{equation}

There is also a trace measure introduced by Austin Fowler which disregards
the global phase factor, so that we don't waste time trying to approximate
the unmeasurable phase of our target gate.

\begin{equation}
d(U,S) = \sqrt{\frac{d - \norm{\mathrm{tr}(U^\dagger S)}}{d}}
\end{equation}

\section{Performance}

Just to get this out of the way, in case you are wondering whether to be
excited or not about Super-Kitaev.

\begin{tabular}{|c|c|c|}
\hline
   & Solovay-Kitaev & Super-Kitaev\\
$L'$ & $O(Ln^{3+\nu})$ & $O(Ln + n^2 \log n)$\\
$d'$ & $O(dn^{3+\nu})$ & $O(d \log{n} + (\log{n})^2))$\\ 
\hline
\end{tabular}

where $\nu$ is a small positive constant.
The remaining parameters are yet to be determined.

\section{History}

In 1995, Seth Lloyd found that almost any two distinct single-qubit rotations are
universal for approximating an arbitrary single-qubit rotation, but that this
approximation could be exponentially long in both time and length $T,L = (O(1/\epsilon))$ \cite{Lloyd1995}.

The theorem which is now called Solovay-Kitaev was discovered by Solovay in
1995 in an unpublished manuscript and independently later discovered by
Kitaev in 1997 \cite{nc00} which showed that $T,L = O(\log^c{1/\epsilon})$ for
$c$ between 3 and 4.

In 2001, Aram completed his undergrad thesis arguing that it would be difficult
to beat $c < 2$ for the above bounds using a successive approximation method.\cite{harrow01}

In 2002, Kitaev, Shen, and Vyalyi published their book which contains an
application of parallelized phase estimation towards simulating a quantum
circuit (what we are calling Super-Kitaev) \cite{ksv02}.
That is, an alternative quantum compiler to Solovay-Kitaev which has
asymptotically better circuit size and depth, but using ancillary qubits
and having as yet unknown multiplicative constants.

In 2003, Aram, Ben Recht, and Ike demonstrated that a certain universal
set could be used to saturate the lower bound $L=O(\log{1/\epsilon})$
but it remains an open problem whether any efficient algorithm exists
which can do this in tractable $T$ \cite{hrc02}.

In 2005, Chris Dawson and Mike Nielsen published their pedagogical review
paper which I used as the basis for my previous work on implementing a
Solovay-Kitaev compiler \cite{Dawson2005}.

\section{Review of Solovay-Kitaev}

Here I'll remind you of the basic pseudo-code for normal Solovay-Kitaev.
Our development is taken from the excellent review paper \cite{Dawson2005}.

\begin{algorithmic}[1]
\STATE \textsc{function} $\tilde{U}_n \leftarrow$ SOLOVAY-KITAEV$(U,n)$
\IF{$n == 0$}
\STATE $\tilde{U}_n \leftarrow $ BASIC-APPROX$(U)$
\ELSE
\STATE $\tilde{U}_{n-1} \leftarrow$ SOLOVAY-KITAEV$(U, n-1)$
\STATE $A,B \leftarrow $ FACTOR$(U\tilde{U}^\dagger_{n-1})$
\STATE $\tilde{A}_{n-1} \leftarrow $ SOLOVAY-KITAEV$(A, n-1)$
\STATE $\tilde{B}_{n-1} \leftarrow $ SOLOVAY-KITAEV$(B, n-1)$
\STATE $\tilde{U}_n \leftarrow \tilde{A}_{n-1}\tilde{B}_{n-1}\tilde{A}^\dagger_{n-1}\tilde{B}^\dagger_{n-1}\tilde{U}_{n-1}$
\ENDIF
return $\tilde{U}_n$
\end{algorithmic}

This algorithm works by way of recursive, successive approximation.

The BASIC-APPROX function above does a lookup (via some kd-tree search
maneuvers through higher-dimensional vector spaces) using the results of
precompiled sequences from the instruction set $\mathcal{G}$. This can be
done offline and reused across multiple runs of the compiler, assuming
$\mathcal{G}$ for your quantum computer doesn't change.

The FACTOR function performs a balanced group commutator decomposition,
$U = ABA^\dagger B^\dagger$, and then recursively approximates the $A$ and $B$
operators using Solovay-Kitaev. Intuitively, when they are multiplied
together again, along with their inverses, their errors (which go like
$\epsilon$) are symmetric and cancel out in such a way that the resulting
product $U$ has errors which go like $\epsilon^2$. In this manner, we can
eventually sharpen our desired error down to any value.

And that's all I'm going to say about that.

\section{The Super-Kitaev Algorithm}

Our development of the Super-Kitaev algorithm follows closely the one in the
book by Kitaev, Shen, and Vyalvi \cite{ksv02}, although of course, it is
simply called Theorem 13.5. Likewise, we will cite the theorem / lemma numbers
from the book, which contains a self-contained description of all the parts
needed for Super-Kitaev.

The basic steps of this method are the following:

\begin{enumerate}
\item Precompiling to get $L'$ gates in $\mathcal{Q} \cup \Lambda(e^{i\phi})$.
Here we see that there is an
efficient decomposition of several important gates into the standard set and
controlled-phase-shifts.
\item Implementing a controlled-phase-shift. This ends up being the hardest
part of simulating a quantum circuit, and requires each of the remaining steps.
\item Use phase estimation of an addition operator to magic states in order to
enact the desired phase shift. This requires both efficient creation of
{\em magic states} and an efficient {\em quantum adder} circuit.
\item Create one magic state, and then make $L'$ copies of it. Use one copy
to simulate each $\Lambda(e^{i\phi})$ gate.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Precompiling to the Standard Set}
\label{subsec:precompile}

In order to perform the precompilation step, we need to know that we can
change any unitary in $SU(d)$ by tensor products of unitaries in $SU(2)$
and $SU(4)$, that is, single- and two-qubit gates.

To prove the universality of the standard set $\mathcal{Q}$ is beyond the
scope of these notes. For our purposes, we assume that we can precompile
any gate down to single-qubit rotations $U \in SU(2)$ and
controlled-single-qubit rotations $\Lambda(U), U\in SU(2)$.
(For example, it's known how to do that for the Toffoli gate, which is what we
need to implement our quantum adder circuit).
From there, how do we get down to the standard set?

%\begin{theorem}[Lemma 8.2]
%\label{lemma82}
%Any arbitrary unitary operator $U$ of dimension $d \times d$ can be represented
%as a product of $d(d-2)/2$ matrices of the form:
%
%\begin{equation*}
%\left( \begin{array}{cccccccc}
%     1 & 0      & \cdots & \cdots & \cdots & \cdots & \cdots & \cdots\\
%     0 & 1      & \cdots & \cdots & \cdots & \cdots & \cdots & \cdots\\
%\vdots & \cdots & \ddots & \cdots & \cdots & \cdots & \cdots & \cdots\\
%\vdots & \cdots & \cdots &      a &      b & \cdots & \cdots & \cdots\\
%\vdots & \cdots & \cdots &      c &      d & \cdots & \cdots & \cdots\\
%\vdots & \cdots & \cdots & \cdots & \cdots & \vdots & \cdots & \cdots\\
%\vdots & \cdots & \cdots & \cdots & \cdots & \cdots & 1 & 0\\
%\vdots & \cdots & \cdots & \cdots & \cdots & \cdots & 0 & 1\\
%\end{array}
%\right)
%\end{equation*}
%
%where $\left( \begin{array}{cc}
%a & b\\
%c & d\\
%\end{array} \right) \in SU(2)$
%\end{theorem}
%
%\begin{proof}
%The running time of this algorithm is $O(M^3) \cdot \mathrm{poly}(\log(1/\delta)$.
%\end{proof}

\begin{theorem}[Problem 8.1]
Any single-qubit gate $U$ can be simulated using $\mathcal{Q} \cup \{ \Lambda(e^{i\phi}) \}$.
\end{theorem}

\begin{proof}
Using the Euler angle decomposition into $X$ and $Z$ rotations, we can express any
unitary $U$ as follows, with real angles $\phi$, $\gamma$, $\beta$, $\alpha$:

\begin{equation}
U = e^{i\phi}e^{i(\gamma/2)\sigma^z}e^{i(\beta/2)\sigma^x}e^{i(\alpha/2)\sigma^z}
\end{equation}
This involves solving four equations in four variables and can be done in constant time.

Now how do we implement each of the elements of the Euler angle decomposition from
the $\mathcal{Q}$? Using these identities:

\begin{equation}
e^{i\phi} = \Lambda(e^{i\phi})\sigma^x\Lambda(e^{i\phi})\sigma^x
\end{equation}
\begin{equation}
\sigma^x = H\Lambda(e^{i\pi})H
\end{equation}
\begin{equation}
e^{i\phi\sigma^z} = \Lambda(e^{-i\phi}\sigma^x\Lambda(e^{i\phi})\sigma^x
\end{equation}
\begin{equation}
e^{i\phi\sigma^x} = H e^{i\phi\sigma^z} H
\end{equation}
\end{proof}

\begin{theorem}[Problem 8.2]
Any controlled operator $\Lambda(U)$ where $U \in SU(2)$ can be simulated using
$\mathcal{Q} \cup \{ \Lambda(e^{i\phi})$.
\end{theorem}

\begin{proof}
We can represent the controlled operator as $\Lambda(U) = \Lambda(e^{i\phi})\Lambda(V)$.
$\Lambda(e^{i\phi})$ is already in our set, so it remains to implement
$\Lambda(V)$, where $V \in SU(2)$. Geometrically, we can decompose any
three-dimensional rotation into two $180^{\circ}$ rotations about appropriate
axes. Using the homomorphism between $SO(3)$ and $SU(2)$ and the fact that
$\sigma^x$ corresponds to a $180^{\circ}$ rotation about the $x$-axis.

\begin{equation}
V = A\sigma^x A^{-1} B\sigma^x B^{-1}
\end{equation}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Controlled-Phase Shift}
\label{subsec:phase-shift}

Now we are down to the standard set $\mathcal{Q}$, plus that pesky
controlled-phase-shift gate $\Lambda{e^{i\phi}}$. This is in general a hard
gate to implement, and one of the reasons why we need a quantum compiler in
the first place!

We could just use normal Solovay-Kitaev and find some sequence of $X$ and
$Z$ gates which implement $\Lambda{e^{i\phi}}$, but that wouldn't be any
fun and we would have no reason to bring in all this extra machinery to
do Super-Kitaev.

Note that in general we can't exactly implement $\Lambda{e^{i\phi}}$ but we
can approximate it as $\Lambda{e^{2\pi i l / 2^n}}$, where $l$ is an integer.
In general this is a special case of the following operator
defined by Kitaev in the following lemma.

\begin{theorem}[Lemma 13.4]
The operator 
$\Upsilon_n(e^{2\pi i / 2^n}) : \ket{l} \rightarrow e^{2\pi i l / 2^n} \ket{l}$
for $0 \le l < 2^n$ can be realized with precision $\delta = 2^{-n}$ by an
$O(n^2 \log n)$-size $O((\log n)^2)$-depth circuit over the standard basis
using ancillas.
\end{theorem}

\begin{proof}
To get started, we will need to introduce a magic state $\ket{\psi}$ with the
integer parameters $n$ and $k$ such that

\begin{equation}
\ket{\psi_{n,k}} = \frac{1}{\sqrt{2^n}-1} \sum_{j=0}^{2^n-1} e^{2\pi i j k / 2^n} \ket{j}
\end{equation}

where $0 \le k < 2^n$, $k$ is odd.

What is interesting to note about this state is that we can enact a phase
shift simply by doing addition. In fact, addition is so useful in Super-Kitaev
that we will later discuss a parallelized adder circuit which, however,
is generic enough to be useful in other quantum algorithms.

%What we need instead is to make use of the index-dependent
%phases of each state, and addition to move to the right phase that we want,
%and easy creation of a superposition of these magic states.

Note that this magic state is an eigenstate of the addition operator defined
by $A : \ket{j} \rightarrow \ket{(j+1) mod 2^n}$
 
\begin{equation}
A\ket{\psi_{n,k}} = e^{2\pi i \phi_k / 2^n} \ket{\psi_{n,k}}
\end{equation}

where finding the eigenvalue $e^{2\pi i \phi_k}$ corresponds to finding
the phase $\phi_k = k / 2^n$

Repeated application of $A$ (say $p$ times) would result in a phase
added to the eigenstate equal to a multiple of $e^{2\pi i p / 2^n}$

\begin{equation}
A^p\ket{\psi_{n,k}} = e^{2\pi i \phi k / 2^n} \ket{\psi_{n,k}}
\end{equation}

To realize our desired operator $\Upsilon_n{e^{2\pi i / 2^n}}$ it suffices
to use the value of $l$ to compute $p$ and then apply the operator:

\begin{equation}
\Upsilon_n(X) : \ket{p,j} \rightarrow \ket{p, (j+p) \mod 2^n}
\end{equation}

for $p,j \in {0,\ldots,2^n-1}$. That is, two $n$-qubit registers contain
the values $p$ and $j$.

Ideally, we would just create $\ket{\psi_{n,k}}$ for some particular $k$
($k=1$ would be ideal). Then we would know exactly which $\ket{\psi_{n,k}}$
we had, and how many times $p$ to apply the $A$ operator
to enact the desired phase shift, where $p$ is the solution to the
following equation:

\begin{equation}
\label{eqn:kp}
kp \equiv l (\mod 2^n)
\end{equation}

Note that we stipulate $k$ to be odd so that there is a unique solution $p$.

Recall now that the magic states $\ket{\psi}$ look suspiciously like a
Quantum Fourier Transform state of the computational basis.
However that doesn't help us here, because QFT is way too complicated to use as
our basic compiler. This is intuitively why these states are hard to create.
If we were able to construct them easily, we would also have a quicker way
of implementing QFT.

However, what we can do is create a superposition over all odd $k$ in the
following way:

\begin{equation}
\ket{\eta} = \normtwo \ket{0} - \normtwo \ket{2^{n-1}} =
\frac{1}{\sqrt{2^{n-1}}} \sum_{s=1}^{2^{n-1}} \ket{\psi_{n,2s-1}}
\end{equation}

Now then here are the required steps.

\begin{enumerate}
\item Create the state $\ket{\eta}$ by starting in the state $\ket{0}^{\otimes n}$,
applying a Hadamard to the most significant qubit to get an equal mix of $\ket{0}$
and $\ket{1}$, then put a negative sign on the $\ket{1}$ component by applying
$\sigma^z$ to the same qubit.
\item Measure $k$ by determining the phase $\phi_k = k/2^n$ with precision
$\delta = 2^{-n}$ by using phase estimation. One of the $n$-qubit registers
now contains $\ket{\psi_{n,k}}$ for some fixed $k$.
This is done by a circuit of size $O(n^2)$ and depth $O(\log n)$.
\item Solve for $p$ as a function of $k$ and $l$ satisfying Equation \ref{eqn:kp}
\item Apply $X^p$ to the $n$-qubit register containing $\ket{\psi}$, which
enacts the desired phase shift.
\item Reverse the first three steps to uncompute $p$
\end{enumerate}

Note that we skimmed over the solution to Equation \ref{eqn:kp} even though this
is the most resource-intensive part of the algorithm. Rest assured, it reduces
to division (or computing the inverse of $2s-1 \mod 2^n$) which Kitaev
provides an efficient solution to as Problem 2.14a in his book.

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Main Algorithm}
\label{subsec:main}

Now assuming we have parallelized phase estimation as a black box, here are
the steps to the Super-Kitaev algorithm.

\begin{theorem}[Theorem 13.5]
Any circuit $C$ of size $L$ and depth $d$ over a fixed finite basis can be
simulated with precision $\delta$ by an $O(Ln + n^2\log n)$-size
$O(d \log n + (\log n)^2)$-depth circuit $C'$ over the standard basis, where
$n = O(\log(L/\delta))$.
\end{theorem}

\begin{proof}

For the steps below, we note that we can avoid solving the equation $kp \equiv l (mod 2^n)$
if we set $k=1$. This is equivalent to realizing $\Upsilon_n(e^{2\pi i / 2^n})$
by applying $\Upsilon(A)$ from Section \ref{subsec:phase-shift} to the state
$\ket{\psi_{n,1}}$. So we need to create one copy of this magic state to
simulate each $\Lambda(e^{i\phi})$ gate, possibly up to $L'$ of them.

\begin{enumerate}
\item Precompile the circuit into gates from $\mathcal{Q} \cup \{\Lambda(e^{i\phi})\}$
using the results from Section \ref{subsec:precompile}.
\item Create the state magic state $\ket{\psi_{n,0}} = H^{\otimes n}\ket{0^n}$
\item Turn it into $\ket{\psi_{n,1}} = \Upsilon(e^{-2\pi i / 2^n}) \ket{\psi_{n,0}}$
using the procedure in Section \ref{subsec:phase-shift}
This is done with a circuit of size $O(n^2\log n)$ and $O((\log n)^2)$ depth.
\item Make $L'$ copies of the state $\ket{\psi_{n,1}}$ out of one copy by 
apply the addition operation below.
\item Simulate the circuit $C'$ using one copy of $\ket{\psi_{n,1}}$ per gate,
this takes size $O(n)$ and depth $O(\log n)$.
\item Reverse the first three steps.
\end{enumerate}

To copy the state $\ket{\psi_{n,k}}$ it suffices to apply the following
operator:

\begin{equation}
\ket{\psi_{n,k}}^{\otimes m} = W^{-1}\left( \ket{\psi_{n,0}}^\otimes(m-1) \otimes \ket{\psi_{n,k}} \right)
\end{equation}

where $W$ is defined by

\begin{equation}
W : \ket{x_1,\ldots,x_{m-1},x_m} \rightarrow \ket{x_1,\ldots,x_{m-1},x_1+\ldots+x_m}
\end{equation}

\end{proof}

\bibliography{report}
\bibliographystyle{tocplain}

\end{document}
