\subsection{Narrowing Function Tables by Inputs}
\label{subsec:narrow}

Now that we have copied enough inputs to source, we can use them
to narrow our function tables (both $f$ and $g$) by successively
halving the function tables based on the value of each
input bit. This is where we rely on our classical control to encode
the function tables in the Toffoli's applied in the narrowings. The function
table itself appears nowhere else in our circuits.

Therefore, each of the $k_i$ input bits takes two Toffoli's,
one of which has a NOT gate to negate its control bit. This
successive halving takes the following number of ancillae, since we start
with a function table of $2^{k_i + k_s}$ and want to end with a function
table of $2^{k_s}$:

\begin{displaymath}
2^{k_i + k_s - 1} + 2^{k_i + k_s - 2} + \ldots + 2^{k_s + 1} + 2^{k_s}
\end{displaymath}

which we can express as the difference of sums:

\begin{displaymath}
\sum_{j=0}^{k_i + k_s - 1} 2^j - \sum_{j=0}^{k_s} 2^j = 
\left( 2^{k_i+k_s} - 1 \right) - \left( 2^{k_s+1} - 1 \right)
\end{displaymath}

Likewise if we use the output function $g$, we can treat each of its
$k_o$, output bits as a separate one-bit output function, and then we
require the same number of gates and ancillae as above for each one.

There is one such narrowed table copy of $f$ (and $g$) for each of $n$ inputs.
For each copy of the table, for each of $k_i$ successive narrowings and
input bits, there are several gates that need to be applied serially because
they use the same control bits---this makes up the circuit depth.
These serial gates are one Toffoli for each of $w(\cdot)$ one outputs,
$z(\cdot)$ of which require single-qubit NOT gates to negate their control.
There is also a factor
of 2 for uncomputing all of these ancillae back to $\ket{0}$.

\begin{table}
\begin{center}
\begin{tabular}{|r|cc|}
\hline
NOT Gates per Input & $\ell_N = $ & $[z(f)+z(g)] \cdot (2^{k_i+k_s} - 2^{k_s+1}) \cdot 2$ \\
Toffoli Gates per Input & $\ell_T = $ & $[w(f)+w(g)] \cdot (2^{k_i+k_s} - 2^{k_s+1}) \cdot 2$\\
Ancillae & & $n\cdot (2^{k_i+k_s} - 2^{k_s+1}) \cdot (1 + \delta_g2\cdot k_o) \cdot 2$\\
Circuit Depth & & $\ell_T d_T + \ell_N d$\\
\hline
\end{tabular}
\caption{Resource counts for Step 2: narrowing function tables by inputs in parallel}
\end{center}
\end{table}