\section{The Main Algorithm}
\label{sec:main-algo}

The Super-Kitaev algorithm takes a radically different approach than
Solovay-Kitaev by identifying that most gates can be easily reduced to
$\mathcal{G}$ in constant time with the exception of the ``targetless''
controlled phase operator, which will take some sweat to approximate.

\begin{displaymath}
\Lambda(e^{i\phi}) = 
 \left(
  \begin{array}{cc}
    1 & 0 \\
    0 & e^{i\phi} \\
  \end{array} \right)
\end{displaymath}

Thankfully \cite{ksv02} is a self-contained reference
for enacting $\Lambda(e^{i\phi})$ with several modules which are useful in
their own right:
parallelized phase estimation procedure, parallel iteration of finite
automata, and a logarithmic depth quantum arithmetic operations such
as addition (and subtraction) described in \ref{subsec:add},
multiplication described in \ref{subsec:mult}, and division described
in \ref{subsec:div}.

It is now useful to discuss certain states with magical properties.
Their superposition is easy to form, they are the eigenstates of the
afore-mentioned
addition operator. Used with phase estimation, this would allow us to enact
a random phase shift simply by adding numbers, which is better than not
being able to shift phases at all (or only being able to do it with a
complicated operator). Moreover, it turns out we can copy these states
also using simple addition. These ideas make Super-Kitaev a beautiful result
regardless of the outcome of our later numerical comparisons.

\input{quals-report-magic-state}

%For the steps below, we note that we can avoid solving the equation $kp \equiv l (mod 2^n)$
%if we set $k=1$. This is equivalent to realizing $\Upsilon_n(e^{2\pi i / 2^n})$
%by applying $\Upsilon(A)$ from Section \ref{subsec:phase-shift} to the state
%$\ket{\psi_{n,1}}$. So we need to create one copy of this magic state to
%simulate each of $m$ $\Lambda(e^{i\phi})$ gates, $m \le L'$.


\subsection{Super-Kitaev Steps}

Given a circuit $C$ to compile,

\begin{enumerate}
\item Precompile $C$ into gates from $\mathcal{G} \cup \{\Lambda(e^{2\pi i l / 2^n})\}$
using the results from Section \ref{subsec:precompile} in $O(1)$ time, depth,
and size.
Now we are done with the single-qubit gates and CNOT, and we have computed
the values $\{l_1, \ldots , l_m\}$ that allow us to approximate our
desired $m$
$\Lambda(e^{i\phi})$ gates as $\phi \approx l/2^n$ to within precision
$2^{-n}$.
\item Create the state magic state $\ket{\psi_{n,0}}$ with $n$ Hadamards.
\item Turn it into $\ket{\psi_{n,1}} = \Upsilon(e^{-2\pi i / 2^n}) \ket{\psi_{n,0}}$
using the registered phase shift procedure in Section \ref{subsec:phase-shift}
This is done with a circuit of size $O(n^2\log n)$ and $O((\log n)^2)$ depth.
\item Make $m$ copies of the state $\ket{\psi_{n,1}}$ out of one copy by 
applying the addition operation $A$.
\item Simulate each $\Lambda(e^{2\pi i l / 2^n})$
using one copy each of $\ket{\psi_{n,1}}$, to which we can add our
values $l$ using $\Upsilon(A)$.
This takes size $O(mn)$ and depth $O(\log n)$, since we can enact
all these phase shifts in parallel.
\end{enumerate}

Now for the resource calculations of these individual steps and their
substeps.

\input{quals-report-precompile}

\input{quals-report-phase-shift}

\input{quals-report-phase-estimate}

\input{quals-report-add}

\input{quals-report-mult}

\input{quals-report-div}

